Statistical paradoxes in coronavirus case-counts: selection bias, measurement error, and the COVID-19 pandemic

### 2021-08-18 write-up/covid-writeup.tex
adding variance and then done

\textcolor{red}{
While the model-based estimates appear more reasonable, note that the estimate on the last week of April is 0.25\% which is a severe underestimate. Caution is therefore warranted when interpreting these estimates.  We know that the age-specific infection fatality rate is likely time-varying and may vary by other factors beyond age.  Therefore, improvements could be made by more finely grained, and accurate IFR estimates; however, there is currently minimal publicly available data to do so.  Moreover, the (thankfully) low number of deaths per strata make uncertainty in these estimates quite high.  Finally, the doubly robust estimates appear similar to the IPW estimate.
}

\begin{figure}[!th]
\centering
\includegraphics[width=.6\linewidth]{../figs/tv_air.png}
\caption{Active Infection Rate Estimates}
\label{fig:air}
\end{figure}

\textcolor{red}{
We also construct ratio and effective reproduction number estimates as discussed in Section XX. Figure XX presents the results.  Unweighted, IPW, and doubly robust estimates appear similar.  Recall the severe bias during the growth phase due to selection bias dicussed in SEction XX may imply the observed rates are severely overestimated between October 2020 and January 2021.  The model-based methods may be conservative in this time window.  A similar argument holds for the effective reproduction rate in Figure XXb.
}

>>>>

While the model-based estimates appear more reasonable, note that the estimate on the last week of April is 0.25\% which is a severe underestimate compared to the estimated prevalence using the stratified random sample. Caution is therefore warranted when interpreting these estimates.  We know that the age-specific infection fatality rate is likely time-varying and may vary by other factors beyond age.  Therefore, improvements could be made by more finely grained, and accurate IFR estimates; however, there is currently minimal publicly available data to do so.  Moreover, the (thankfully) low number of deaths per strata make uncertainty in these estimates quite high.  Finally, the doubly robust estimates appear similar to the IPW estimate.

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{../figs/tv_air.png}
  \caption{Active Infection Rate Estimates}
  \label{fig:air}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
 \centering
 \includegraphics[width=.9\linewidth]{../figs/tv_air_ratio.png}
 \caption{Ratio estimates}
 \label{fig:air_ratio}
\end{subfigure}
\caption{Time-varying estimates based on unweighted, model-based, IPW and doubly robust methods.}
\label{fig:tvestimates}
\end{figure}

We also construct ratio estimates as discussed in Section~\ref{section:rates}. Figure~\ref{fig:air_ratio} presents the results.  Unweighted, IPW, and doubly robust estimates appear similar.  Recall the severe bias during the growth phase due to selection bias dicussed in Section~\ref{section:rates} may imply the observed rates are  overestimated between October 2020 and January 2021.  The model-based methods may be as well.
